\subsection{Lower House Election Disproportionality}\label{subsec_view_lhelc_lsq}

View \texttt{view\_lhelc\_lsq} is based on tables Lower Houses, LH Elections, LH Vote Results and LH Vote Results, and provides data at the level of lower house elections.

It computes Gallagher's Least-square index (LSq) according to \citet{Gallagher1991}, which measures the dispoportionality in the distribution of seats in a lower house election: 
\begin{equation}\label{LSq_equation}
\mbox{LSq}_{\mbox{\tiny Gallagher}}=\sqrt{\frac{1}{2}\sum\limits_{j=1}^{J} (v_{j}-s_{j})^{2}},
\end{equation}
where $j$ denotes parties, $v$ vote and $s$ seat shares gained in an election to the lower house. 

The LSq weighs the deviations of seat from vote shares by their own value, creating a index ranging from zero to 100. 
The lower the index value, the lower the disproportionality and vice versa. 

Note that seat results that stem from lower houses elections constitute only a subset of all seat results,
because a lower house configuration may not only result from a lower house election, but also from party splits or mergers.
Therefore, the disporportionality figures are provided at the lower house election, so that they can be joined on the first-mentioned, larger subset of lower house configurations.


View \texttt{view\_lhelc\_lsq} is defined as follows:
\lstinputlisting[%caption={Code to compute Gallagher's LSq index of disproportionality in lower houses.},%
language=SQL]%
{../SQL-codes/views/view_lhelc_lsq.sql}

Note that variable \texttt{lhelc\_lsq\_computed} cannot be computed for lower house elections in which (a) for at least one party with seat(s) in the lower house neither proportional nor plurality vote results are recorded, or (b) neither proportional nor plurality seats are recorded, even though the party is not identified as 'Other without seat', i.e. \texttt{pty\_id} is not \#\#999.
%Consistency check \texttt{cc\_missing\_lhelc\_pty\_sts\_records} (\ref{cc_missing_lhelc_pty_sts_records}) enlists all party-election configurations to which one or boths applies.

The PCDB also includes the variable \texttt{lhelc\_lsq\_noothers\_computed}, which excludes the vote and seat shares listed for the category `Others with seats' from computing the LSq. 
The definition of view \texttt{view\_lhelc\_lsq\_noothers} is provided in the Appendix (see \ref{subsec_appx_view_lhelc_lsq_noothers}).